%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.7in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape VIKASH PANDA} \\ \vspace{2pt}
    {\large \textit{Software Developer $|$ Computer Science Engineer $|$ Web Developer}} \\ \vspace{3pt}
    \small \raisebox{-0.1\height}\faPhone\ +91-9937666626 ~
    \href{mailto:vpanda803@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{vpanda803@gmail.com}} ~
    \href{mailto:vikash@thepanda.fyi}{\raisebox{-0.2\height}\faEnvelope\ \underline{vikash@thepanda.fyi}} ~
    \raisebox{-0.1\height}\faMapMarker\ Cuttack, Odisha, India
\end{center}
\vspace{-6pt}

%-----------SUMMARY-----------
\section{Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    B.Tech Computer Science graduate with strong foundations in \textbf{Data Structures and Algorithms (DSA), Data Analytics, and Data Science}. Proficient in \textbf{Java, C++, Python, HTML5, and CSS3} with hands-on frontend web development experience. Brings a proven \textbf{8-year track record of teaching 100+ students}, achieving a \textbf{95\% success rate} (85\%+ in ICSE/CBSE board exams). A self-driven, articulate professional with strong \textbf{communication, mentorship, and problem-solving} skills.
  }}
\end{itemize}
\vspace{-14pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Ajay Binay Institute of Technology (ABIT), Cuttack}{September 2021 -- August 2025}
      {Bachelor of Technology --- Computer Science and Engineering (B.Tech CSE)}{}

    \resumeSubheading
      {JKBK Government High School, Cuttack}{April 2019 -- May 2021}
      {Higher Secondary (Class XII) --- Science}{88.67\%}

    \resumeSubheading
      {Stewart School, Cuttack}{March 2007 -- April 2018}
      {Secondary (ICSE, Class X)}{87.83\%}

  \resumeSubHeadingListEnd
\vspace{-14pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Private Academic Tutor}{June 2018 -- June 2026}
      {\textbf{Mathematics \& Science Tutor --- ICSE \& CBSE (Class VIII--X)}}{\textbf{Cuttack, Odisha}}
      \resumeItemListStart
        \resumeItem{Tutored \textbf{100+ students} across ICSE and CBSE boards (Class VIII--X) over 8 years, with \textbf{95\% scoring above 85\%} in Matriculation board examinations.}
        \resumeItem{Designed \textbf{personalised learning plans} for each student, identifying weak areas and applying targeted practice strategies that led to measurable, consistent grade improvements.}
        \resumeItem{Delivered \textbf{concept-first teaching} using real-world examples to build strong academic foundations and exam confidence; several students advanced to top Science colleges.}
        \resumeItem{Independently managed scheduling, parent communication, and progress tracking — demonstrating \textbf{ownership, accountability, and long-term professional commitment}.}
      \resumeItemListEnd

    \resumeSubheading
      {SkillGigs}{November 2024 -- February 2025}
      {\textbf{Marketplace Coordinator}}{\textbf{Remote}}
      \resumeItemListStart
        \resumeItem{Coordinated marketplace operations between clients and candidates on the SkillGigs platform, ensuring smooth onboarding, communication, and timely resolution of queries.}
        \resumeItem{Rapidly adopted and became proficient in \textbf{HubSpot CRM, Google Workspace, and Microsoft Teams} — and proactively \textbf{trained colleagues} on their effective use, improving team-wide productivity.}
        \resumeItem{Demonstrated strong \textbf{cross-functional communication and leadership} by bridging gaps between stakeholders and ensuring alignment across operational workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {Kaustubh Medtech}{June 2023 -- July 2023}
      {\textbf{Web Development Intern}}{\textbf{Hyderabad, Telangana}}
      \resumeItemListStart
        \resumeItem{Designed and developed \textbf{responsive frontend templates} for the company's official website using \textbf{HTML, CSS, and JavaScript}, improving user experience and visual consistency.}
        \resumeItem{Collaborated in an \textbf{Agile team environment}, iterating on UI/UX feedback and delivering modules on schedule within a fast-paced product workflow.}
        \resumeItem{Strengthened understanding of real-world \textbf{product development workflows} by actively participating in design reviews and implementing cross-browser compatible layouts.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-14pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
        {\textbf{Personal Portfolio Website} $|$ \emph{HTML5, CSS3, JavaScript}}{2024}
        \resumeItemListStart
          \resumeItem{Built a \textbf{fully responsive portfolio} with clean layouts, CSS animations, and semantic HTML — compatible across all devices and optimized for accessibility.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Student Performance Data Analysis} $|$ \emph{Python, Pandas, Matplotlib}}{2024}
        \resumeItemListStart
          \resumeItem{Performed \textbf{EDA} on a real-world dataset — cleaned, transformed, and visualized data to surface key factors affecting student academic outcomes.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd
\vspace{-14pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages \& Web}{: Java, C++, Python, JavaScript, HTML5, CSS3, Responsive Design} \\
     \textbf{Data \& Analytics}{: Data Structures \& Algorithms (DSA), Data Analytics, Data Science, Pandas, Matplotlib, EDA} \\
     \textbf{Tools}{: Git, GitHub, VS Code} \\
    }}
 \end{itemize}
\vspace{-14pt}

%-----------ACHIEVEMENTS-----------
\section{Achievements \& Activities}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Academic Excellence}{: \textbf{87.83\%} in ICSE (Class X) and \textbf{88.67\%} in Class XII Science --- consistent high performance throughout schooling.} \\
     \textbf{Oratory \& Communication}{: Proficient public speaker with strong English skills; participated in college-level debates and presentations.} \\
    }}
 \end{itemize}

\end{document}
